|

### 2023-01-22 paper_comparison/paper_comparison/paper_comparison.Rmd
modify plot for different b

\begin{gather}  \label{eq:effect-size}
E = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V})|}{|diag(\boldsymbol{R}_a\sigma^2)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V})^{-1}diag(\boldsymbol{R}_a\sigma^2)) + \boldsymbol{\mu}_z^{T}(\boldsymbol{R}_a\boldsymbol{V})^{-1}\boldsymbol{\mu}_z\right),\\
\boldsymbol{R}_a = \boldsymbol{I}_n - \boldsymbol{H}_a,
\boldsymbol{H}_a = \boldsymbol{X}_a(\boldsymbol{X}_a^T\boldsymbol{X}_a)^{-1}\boldsymbol{X}_a^T,
\end{gather}

@@

# Generate data for b = 0.25
ori_dat <- heter_model(a = 0, 
                       x = {
                         raw_x <- rand_uniform(-1, 1);
                         closed_form(~stand_dist(raw_x))
                         }, 
                       b = 0.25)$gen(300)

# Plot data for b = 0.25
bp1 <- VI_MODEL$plot(ori_dat) +
  ggtitle(quote("b = 0.25")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for b = 1
bp2 <- heter_model(a = 0, 
                   x = {
                     raw_x <- rand_uniform(-1, 1); 
                     closed_form(~stand_dist(raw_x))
                     }, 
                   b = 1)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote("b = 1")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for b = 4
bp3 <- heter_model(a = 0, 
                   x = {
                     raw_x <- rand_uniform(-1, 1); 
                     closed_form(~stand_dist(raw_x))
                     }, 
                   b = 4)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote("b = 4")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate data and plot data for b = 16
bp4 <- heter_model(a = 0, 
                   x = {
                     raw_x <- rand_uniform(-1, 1); 
                     closed_form(~stand_dist(raw_x))
                     }, 
                   b = 16)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote("b = 16")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate data and plot data for b = 64
bp5 <- heter_model(a = 0, 
                   x = {
                     raw_x <- rand_uniform(-1, 1); 
                     closed_form(~stand_dist(raw_x))
                     }, 
                   b = 64)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote("b = 64")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

patchwork::wrap_plots(bp1, bp2, bp3, bp4, bp5, ncol = 5)
```

>>>>

\begin{gather}  \label{eq:effect-size}
E = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V})|}{|diag(\boldsymbol{R}_a\sigma^2)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V})^{-1}diag(\boldsymbol{R}_a\sigma^2)) + \boldsymbol{\mu}_z^{T}(\boldsymbol{R}_a\boldsymbol{V})^{-1}\boldsymbol{\mu}_z\right),\\
\boldsymbol{R}_a = \boldsymbol{I}_n - \boldsymbol{H}_a,\\
\boldsymbol{H}_a = \boldsymbol{X}_a(\boldsymbol{X}_a^T\boldsymbol{X}_a)^{-1}\boldsymbol{X}_a^T,
\end{gather}

@@

# Generate data for b = 0.25
dat_b025 <- heter_model(a = 0, 
                        x = {
                          raw_x <- rand_uniform(-1, 1);
                          closed_form(~stand_dist(raw_x))
                          }, 
                        b = 0.25)$gen(300) %>%
  mutate(b = "b: 0.25")

# Generate data for other b
map(c(1, 4, 16, 64), function(b) {
  heter_model(a = 0,
              x = {
                raw_x <- rand_uniform(-1, 1); 
                closed_form(~stand_dist(raw_x))
                }, 
              b = b)$
  gen(300, computed = select(dat_b025, x, e)) %>%
  mutate(b = paste0("b: ", b))
}) %>%

  # Combined with data for b = 0.25
  bind_rows(dat_b025) %>%
  mutate(b = factor(b, levels = paste0("b: ", c(0.25, 1, 4, 16, 64)))) %>%
  VI_MODEL$plot() +
  facet_wrap(~b, scales = "free", ncol = 5) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())
```
